Galois Transformers and Modular Abstract Interpreters

### 2015-03-26 writeup/oopsla2015.tex
hit the page limit exactly

We solve the problem of systematically constructing static analyzers by
introducing \emph{Galois transformers}: monad transformers that
transport Galois connection properties.  In concert with a monadic
interpreter, we define a library of monad transformers that
implement building blocks for classic analysis parameters like context, path,
and heap (in)sensitivity. Moreover, these can be composed together 
% to realize a program analysis monad, 
\emph{independent of the language being analyzed}.

>>>>

We solve the problem of systematically constructing static analyzers by
introducing \emph{Galois transformers}: monad transformers that
transports Galois connection properties.  In concert with a monadic
interpreter, we define a library of monad transformers that
implement building blocks for classic analysis parameters like context, path,
and heap (in)sensitivity. Moreover, these can be composed together 
% to realize a program analysis monad, 
\emph{independent of the language being analyzed}.
